Voice Classification by Neural Networks

### 2015-05-27 paper.tex
Methodology section completed up to Fourier

\title{Voice Classification by Neural Networks}
\author{Tony Zhang, James Tsui, Maryam Bahrani}

@@

% why do we want it? +overfitting
% training/test data
%

@@

>>>>

\title{Voice Classification by Neural Networks}
\author{
	\href{mailto:txz@mit.edu}{Tony Zhang},
	\href{mailto:jtsui@hotchkiss.org}{James Tsui},
	\href{mailto:mbahrani@hotchkiss.org}{Maryam Bahrani}
}

@@

% why do we want it? +overfitting
% training/test data

@@

Subjects were selected based on availability, with a majority of participants being students of the Hotchkiss School.
Voice recordings were collected from a total of $n = 63$ subjects (27 male and 36 female).

Subject voice data was obtained in the form of 22050 Hz \texttt{.aiff} files, recorded using the microphone of an iPhone.
Subjects were instructed to speak until they were told to stop, and an approximately 10 second recording of their speech was made.
The sex and age of the subjects were recorded.
Although recorded, subject’s age is likely to be insignificant due to the stabilization of most voices post-puberty. Some subjects were given novels and other reading material to read from, as they were uncomfortable with speaking without directives.
This data was collected in relatively silent locations, thus minimizing background or stray noises.

All data processing and analysis was completed in Wolfram Mathematica.
The voice samples were imported and processed using Fourier analysis.
We experimented with multiple schemata for feature extraction, before ultimately settling on the best for our purposes.
Each voice sample was broken into 0.5 second fragments (any trailing data at the end of the sound sample was discarded).
We took the norms of the discrete Fourier transform (DFT) of each fragment and added them together (i.e. if fragments $1, 2, \dots, n$ have DFTs $\hat{f_1},\hat{f_2}, \dots, \hat{f_n}$, we find $g = \sum_k |\hat{f_k}|$). The resulting function $g$ was normalized as in \[\bar{g} = \frac{g}{\sum\limits_m g(m)}\] where we sum over all $m$ in the (finite) domain of $g$.\footnote{As we are working with half-second fragments of 22050 Hz sound files, this domain is actually $\frac{\ZZ}{11025\ZZ}$.} Each voice file was analyzed thus, and a series of features were generated for each; these features constituted a profile of each subject's voice.
